Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-05-17 prop_letter.tex
pass over entire paper

When combining non-disjoint events, there is a further subtlety whose
resolution will give the most general and final condition as
follows. For general, non-necessarily disjoint events $E_1$ and $E_2$,
we have:
\begin{equation}
\mu(E_1+E_2) + \mu(E_1E_2) \subseteq \mu(E_1) + \mu(E_2)
\label{eq:classicalconvex}
\end{equation}
which is a generalization of the classical inclusion-exclusion
principle that uses $\subseteq$ instead of $=$ for the same reason as
before. The new condition, known as \emph{convexity}, reduces to the
previously motivated condition when the events are disjoint, i.e.,
when $\mu(E_1E_2) = 0$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage  
\section{Rest of Paper}

@@

 In general, measurements done with limited resources and poor precision
may not uniquely identify the true state of a classical system. However,
at least one system is consistent with the measurements when the system
satisfies an extra-condition called convex.

\begin{definition}
$\bar{\mu}$ is called convex~\cite{Griffiths2003}. if for all
commuting $P_{0},P_{1}\in\events$, we have
$\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
\end{definition}

Based on Shapley's classical result~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016},
we have the following theorem.

\begin{thm}\label{thm:Shapley}For every convex quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
if a sub-event space~$\events'\subseteq\events$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}

@@

Gleason's theorem asserts any quantum real-valued probability measure
is consistent with a unique mixed state, and Shapley proved a convex
quantum IVPM must approximate some states for each classical sub-event
space. However, it may not approximate the same state in every sub-event
space. As the result, there may be no state consistent with a convex
quantum IVPM on all projectors~$\events$.

\begin{example}\label{ex:three-dimensional-three-value}Given a three
dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Let $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
$\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$, $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$,
and
\begin{subequations}
\begin{eqnarray}
 &  & \begin{aligned}\imposs & =\bar{\mu}_{3}(\mathbb{0})=\bar{\mu}_{3}(\proj{0})\\
 & =\bar{\mu}_{3}(\proj{\ps})=\bar{\mu}_{3}(\proj{\ps'})\textrm{ ,}
\end{aligned}
\\
 &  & \begin{aligned}\necess & =\bar{\mu}_{3}(\mathbb{1})=\bar{\mu}_{3}(\mathbb{1}-\proj{0})\\
 & =\bar{\mu}_{3}(\mathbb{1}-\proj{\ps})=\bar{\mu}_{3}(\mathbb{1}-\proj{\ps'})\textrm{ ,}
\end{aligned}
\\
 &  & \unknown=\bar{\mu}_{3}(P)\qquad\textrm{otherwise.}
\end{eqnarray}
\end{subequations}
It is straightforward to verify that $\bar{\mu}_{3}$ is a convex
quantum IVPM.

Similarly, let $S_{2}=\left\{ \proj{0},\proj{\ps'}\right\} $. We
have $\coreBorn\left(\bar{\mu}_{3},S_{2}\right)=\left\{ \proj{1}\right\} $.
Therefore, 
\begin{equation}
\coreBorn\left(\bar{\mu}_{3},\events\right)\subseteq\coreBorn\left(\bar{\mu}_{3},S_{1}\right)\cap\coreBorn\left(\bar{\mu}_{3},S_{2}\right)=\emptyset
\end{equation}
and must be empty.\end{example}

Although Gleason's theorem doesn't hold for every quantum IVPM, it
can be applied in a limit case when the intervals are infinitely precise.
That is, when $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
any quantum IVPM can be recast as an real-valued one and has an unique
state consistent with it on every projector when $d\ge3$.

>>>>

When combining non-disjoint events, there is a further subtlety whose
resolution will give the most general and final condition as
follows. For general, non-necessarily disjoint events $E_1$ and $E_2$,
we have:
\begin{equation}
\mu(E_1+E_2) + \mu(E_1E_2) \subseteq \mu(E_1) + \mu(E_2)
\label{eq:classicalconvex}
\end{equation}
which is a generalization of the classical inclusion-exclusion
principle that uses $\subseteq$ instead of $=$ for the same reason as
before. The new condition, known as
\emph{convexity}~\cite{Griffiths2003}, reduces to the previously
motivated condition when the events are disjoint, i.e., when
$\mu(E_1E_2) = 0$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Gleason}

In the classical setting, measurements done with limited resources and
poor precision may not uniquely identify the true state of a system
system. However, there is always at least one state that is consistent
with the imprecise
measurements~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}.

\begin{thm}\label{thm:Shapley}
  For every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a
  sub-event space~$\events'\subseteq\events$ commutes, then
  $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.
\end{thm}

Gleason's theorem asserts any quantum real-valued probability measure
is consistent with a unique mixed state, and Shapley proved a quantum
IVPM must approximate some states for each classical sub-event
space. However, it may not approximate the same state in every
sub-event space. As the result, there may be no state consistent with
a quantum IVPM on all projectors~$\events$.

\begin{example}\label{ex:three-dimensional-three-value}
  Given a three dimensional Hilbert space with an orthonormal basis
  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.  Let
  $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
  $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
  $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and
\begin{subequations}
\begin{eqnarray}
 &  & \begin{aligned}\imposs & =\bar{\mu}_{3}(\mathbb{0})=\bar{\mu}_{3}(\proj{0})\\
 & =\bar{\mu}_{3}(\proj{\ps})=\bar{\mu}_{3}(\proj{\ps'})\textrm{ ,}
\end{aligned}
\\
 &  & \begin{aligned}\necess & =\bar{\mu}_{3}(\mathbb{1})=\bar{\mu}_{3}(\mathbb{1}-\proj{0})\\
 & =\bar{\mu}_{3}(\mathbb{1}-\proj{\ps})=\bar{\mu}_{3}(\mathbb{1}-\proj{\ps'})\textrm{ ,}
\end{aligned}
\\
 &  & \unknown=\bar{\mu}_{3}(P)\qquad\textrm{otherwise.}
\end{eqnarray}
\end{subequations}
It is straightforward to verify that $\bar{\mu}_{3}$ is a convex
quantum IVPM.

Similarly, let $S_{2}=\left\{ \proj{0},\proj{\ps'}\right\} $. We have
$\coreBorn\left(\bar{\mu}_{3},S_{2}\right)=\left\{ \proj{1}\right\} $.
Therefore,
\begin{equation}
\coreBorn\left(\bar{\mu}_{3},\events\right)\subseteq\coreBorn\left(\bar{\mu}_{3},S_{1}\right)\cap\coreBorn\left(\bar{\mu}_{3},S_{2}\right)=\emptyset
\end{equation}
and must be empty.
\end{example}

Although Gleason's theorem doesn't hold for every quantum IVPM, it
can be applied in a limit case when the intervals are infinitely precise.
That is, when $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
any quantum IVPM can be recast as an real-valued one and has a unique
state consistent with it on every projector when $d\ge3$.

@@

\begin{definition}
$\bar{\mu}$ is called convex. if for all
commuting $P_{0},P_{1}\in\events$, we have
$\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
\end{definition}

@@
